\problemname{Disastrous Doubling}

% https://en.wikipedia.org/wiki/Bacteria
\illustration{0.25}{ecoli}{Picture by Rocky Mountain Laboratories via Wikipedia}

\newcommand{\modval}{10^9+7}
\newcommand{\maxn}{10^5}
\newcommand{\maxb}{2^{20}}
\newcommand{\errormessage}{error}

% problem
A scientist, E. Collie, is going to do some experiments with bacteria.
Right now, she has one bacterium.
She already knows that this species of bacteria doubles itself every hour.
Hence, after one hour there will be $2$ bacteria.

E. Collie will do one experiment every hour, for $n$ consecutive hours.
She starts the first experiment exactly one hour after the first bacterium starts growing.
In experiment $i$ she will need $b_i$ bacteria.

How many bacteria will be left directly after starting the last experiment?
If at any point there are not enough bacteria to do the experiment, print \texttt{\errormessage}.

Since the answer may be very large, please print it modulo $\modval$.

\begin{Input}
	The input consists of two lines.
	\begin{itemize}
		\item The first line contains an integer $1\leq n\leq \maxn$, the number of experiments.
		\item The second line contains $n$ integers $b_1,\dots,b_n$, where $0\leq b_i\leq \maxb$ is
			the number of bacteria used in the $i$th experiment.
	\end{itemize}
\end{Input}

\begin{Output}
\begin{itemize}\item
	Output a single line containing the number of bacteria that remains after doing all the experiments, or
	\texttt{\errormessage}.
\end{itemize}
\end{Output}
